---
title: "BMI Example"
author: "Michael Sachs"
date: "March 31, 2015"
output: 
    word_document
---

Let's read in the BMI dataset and see what we have to work with. Make sure it is in the same directory as this .Rmd file!

```{r setup}
bmi <- read.csv("BMI.CSV", stringsAsFactors = FALSE)
head(bmi)
summary(bmi)
```

Let's examine the relationship between gender and pack years of smoking. 

```{r ttest, comment = NA}
with(bmi, t.test(packyrs ~ gender))
```

Wow, men tend to smoke much more than women. What is the distribution of pack years of smoking?


```{r smkplot, warning = FALSE, message = FALSE}
library(ggplot2)
ggplot(bmi, aes(x = packyrs)) + geom_bar(stat = "bin")
ggplot(bmi, aes(x = packyrs, fill = gender)) + geom_density(alpha = .5)
```


It appears that there are more women that do not smoke at all (packyears = 0). The proportion of women who do not smoke is `r round(mean(subset(bmi, gender == "FEMALE")$packyears == 0, na.rm = TRUE), 2)`.

```{r table, results = 'asis'}
with(bmi, knitr::kable(table(gender, smoke), caption = "Cross-tabulation of gender by smoking status in the BMI dataset. "))
```
